\subsection{Flan napolitano}

\begin{quote}
\textit{Flan napolitano} is a custard dessert with a layer of soft caramel on top. It is the mexican version of \textit{cr\`eme caramel}. No idea why we call it ``neapolitan", though.
\end{quote}

\underline{Tools}

\begin{itemize}
\item Flan mold ($\sim$1.5 quart)
\item Baking pan bigger than the flan mold
\item Oven
\item Small pot or pan
\item Wood/plastic cooking spoon
\item Small knife
\end{itemize}

\underline{Ingredients}

\begin{itemize}
\item \sfrac{1}{2} cups of sugar
\item 4 eggs
\item 397gr of condensed milk (1 can)
\item 1 cup of evaporated milk
\item 1 tsp of vanilla extract
\item 10 oz of cream cheese
\end{itemize}

\newpage
\underline{Instructions}

\begin{enumerate}
\item Melt the sugar in the small pan. Use a medium size flame and stir continuously.
\item As soon as the last bit of sugar is melted, poor into the bottom of the flan mold.  
\item Let it reach room temperature.
\item Blend the rest of the ingredients and poor into the flan mold, on top on the now crystallized sugar, and close it.
\item Add water to the big baking pan and place the flan mold inside (bain-marie). Sugar goes on the bottom. It will likely float, that's fine.
\item Leave into the preheated oven at 400${}^\circ$F for 1hr.
\item Take it out and let it reach room temperature.
\item Put it in the fridge for a few hours until it gets cold and solid.
\item Open the lid of the flan mold and with the small knife go around the interior walls, so it doesn't stick.
\item Place a flat dish upside down on top of the open mold. Place one hand on the bottom of the mold and the other on top, cross your toes and quickly turn it over.
\item Gently remove the flan mold. Let most of the caramel drip on top, although you won't get all of it.
\item Enjoy!
\end{enumerate}

